### 2016-12-13 paper/evaluation.tex
updated rq2

To evaluate the  use of low-level parallelism, we considered the 91
subjects from the groups \emph{long} and \emph{medium} identified in
Section~\ref{sec:rqone}. In an initial exploration, we searched for
evidences of low-level parallelism settings on configuration files
(\ie, \emph{pom.xml}) from each subject using a semi-automated
approach: we use a script to find all subjects with evidences of
parallel settings and then we manually inspect each configuration file
to eliminate false-positives. Given a list of subjects, our script
searches recursively all \emph{pom.xml} files from the project
directory and uses the command-line tool \emph{grep} to highlight the
presence of the keywords \emph{forkMode}, \emph{forkCount}, and
\emph{parallel}. Any of these keywords exist in any possible
combination of parallel settings (see Section~\ref{sec:modes}). Before
the manual inspection, we found that 37.14\% (13 out of 35) and 62.5\%
(35 out of 56) of subjects from the \emph{long} and \emph{medium}
groups did not have any of the keywords. After the manual inspection
\Fix{...elaborate...}

\Fix{We discovered that \Fix{X}\% and \Fix{y}\%
of subjects (\emph{long} and \emph{medium}, respectively) did not have
any evidence of low-level parallelism. It is important to mention that
this result an upper bound limit since the keyword highlighted could
not be part of a real configuration (\eg, part of a comment). To
investigate further the projects reported by our script, we manually
inspected \Fix{X} configuration files to eliminate false-positives.}
\Fix{...elaborate...}

>>>>

To evaluate the  use of low-level parallelism, we considered the 91
subjects from the groups \emph{long} and \emph{medium} identified in
Section~\ref{sec:rqone}. In an initial exploration, we searched for
evidences of low-level parallelism settings on configuration files
(\ie, \emph{pom.xml}) from each subject using a semi-automated
approach: we use a script to find all subjects with evidences of
parallel settings and then we manually inspect each configuration file
to eliminate false-positives. In addition, we are interested in
understanding how these parallel settings are used. Given a list of
subjects, our script searches recursively all \emph{pom.xml} files
from the project directory and uses the command-line tool \emph{grep}
to highlight the presence of the keywords \emph{forkMode},
\emph{forkCount}, and \emph{parallel}.  Any of these keywords exist in
any possible combination of parallel settings (see
Section~\ref{sec:modes}). From the 91 subjects, our script detected 43
subjects with evidence of parallel settings. After the inspection of
130 configuration files, we confirmed that \Fix{X} settings are real
parallel configurations.  These settings are related to \Fix{Y}
subjects. It is important to notice that, \Fix{X}\% of the subjects
(\emph{medium} and \emph{long} aggregated) did not explore low-level
parallelism according to our criteria of matching keywords. After the
inspection, this rate raises to \Fix{Y}\%. \Fix{elaborate: some
projects doesn't use parallel features, so what?}
Table~\ref{tab:inspection-table} summarizes our initial findings.

\begin{table}[h!]\footnotesize
    \centering
    \begin{tabular*}{0.5\textwidth}{cccc}
        \toprule
        Group  & Subjects with Evidence & Config. Files & Config. Confirmed\\
        \midrule
        Long   & 22 / 35    & 77 / 1981       & \Fix{X} / 77\\%
        Medium & 21 / 56    & 53 / 491        & \Fix{X} / 53\\%
        \midrule 
        Total  & 43 / 91    & 130 / 2472      & \Fix{X} / 130\\
        \bottomrule
    \end{tabular*}
    \caption{\Fix{to-be-defined}}
    \label{tab:inspection-table} 
\end{table}

\Fix{elaborate: write about the subjects that use parallelism - How do
they use them? Would it be possible to measure the benefits? How the
configs from Section~\ref{sec:modes} are distributed?}
